Towards Attack-Tolerant Networks: Concurrent Multipath Routing and the Butterfly Network

### 2017-10-26 www-2018/source/paper.tex
Finish draft of new abs.

\begin{abstract}

It is desirable for critical large-scale communication networks
such as the internet to be resilient against any types of disruption
\cite{sterbenz_resilience_2010}.
Vulnerabilities in communication infrastructure can be used by
state, corporate, and private actors to achieve censorship and surveillance,
to the detriment of free expression and free association
\cite{}.
Self-organized networks such as the internet's router network typically have
heavy-tailed degree distributions
/cite{barabasi_scale-free_2009},
making them resilent against random faults,
but highly vulnerable to targeted attacks against high-centrality nodes
\cite{albert_error_2000}.
Cryptographic solutions fail to address the underlying topological problem,
and remain vulnerable to man-in-the-middle attacks
\cite{nayak_different_2010}
and coercion
\cite{gruel_caveat_2013}.

1 Main result
We present a novel concurrent multipath routing (CMR) algorithm for the wraparound
butterfly network topology,
as well as a highly attack-tolerant
Structured Multipath Fault Tolerance (SMFT) architechture
which incorporaes the butterfly CMR algorithm.

2-3 Main result vs previous knowledge

1-2 General context

2-3 Broader perspective

Targeted attacks against network infrastructure are notoriously difficult
to guard against.
In the case of communication networks,
such attacks can leave users vulnerable to
censorship and surveillance,
even when cryptography is used.
Much of the existing work on network fault-tolerance focuses on random faults and
does not apply to adversarial faults (attacks).
Centralized networks have single points of failure by definition,
leading to a growing popularity in decentralized architectures and protocols
for greater fault-tolerance.
However, centralized network {\em structure} can arise even when {\em protocols} are
decentralized.
Despite their decentralized protocols,
the Internet and World-Wide Web have
been shown both theoretically and historically to be highly susceptible to
attack, in part due to emergent structural centralization.
When single points of failure exist,
they are potentially vulnerable to non-technological
(i.e., coercive) attacks,
suggesting the importance of a structural approach to attack-tolerance.
We show how the assumption of bounded trust transitivity,
while more realistic than the assumption underlying webs of trust,
can be used to quantify the effective redundancy of a network
as a function of trust transitivity.
We also prove that the effective redundancy of the wrap-around butterfly topology
increases exponentially with trust transitivity and
describe a novel concurrent multipath routing algorithm for constructing
paths to utilize that redundancy.
When portions of network structure can be dictated
our results can be used to create scalable,
attack-tolerant infrastructures.
More generally, our results provide a theoretical formalism for evaluating the effects
of network structure on adversarial fault-tolerance.
\end{abstract}

>>>>

\begin{abstract}
It is desirable for critical large-scale communication networks
such as the internet to be resilient against any types of disruption
\cite{sterbenz_resilience_2010}.
Vulnerabilities in communication infrastructure can be used by
state, corporate, and private actors to achieve censorship and surveillance,
to the detriment of free expression and free association
\cite{}.
Self-organized networks such as the internet's router network typically have
heavy-tailed degree distributions
\cite{barabasi_scale-free_2009},
making them resilient against random faults,
but highly vulnerable to targeted attacks against high-centrality nodes
\cite{albert_error_2000}.
Cryptographic solutions fail to address the underlying topological problem,
and remain vulnerable to man-in-the-middle attacks
\cite{nayak_different_2010}
and coercion
\cite{grewal_caveat_2013}.
Coercion-resistant, topological approaches to attack tolerance are needed
to address the current vulnerability of communications infrastructure to
targeted censorship and surveillance.
We present a novel concurrent multipath routing (CMR) algorithm for the wraparound
butterfly network topology,
as well as a highly attack-tolerant
Structured Multipath Fault Tolerance (SMFT) architecture
which incorporates the butterfly CMR algorithm.
Our architecture is the first theoretical demonstration of a
coercion-resistant point-to-point communication architecture
that does not require infinitely transitive trust.
We also present for modeling attack-tolerance as a function of
trust transitivity,
and show how the internet's router network could be rewired for greater
attack-tolerance.
We identify a previously unexplored relationship between
network topology, trust transitivity, and attack-tolerance,
and provide a framework for further exploration of this relationship.
Our results are the first we're aware of to demonstrate
that large-scale communication networks can be
designed to tolerate targeted attacks,
including coercion and other non-technical attacks.
Furthermore, if attack-tolerance requirements are strict enough to justify
a high level of control over network topology, our results could be applied
directly.
More broadly, we hope that this work will serve as a starting point for the
development of additional topology-based attack-tolerant
communication architectures to guard
against the dangers of censorship and surveillance.
\end{abstract}
